\subsection{Unit of Work}\label{sec:unit_of_work}

A unit of work defines the metric by which progress toward completing a program's execution is measured. 
It must remain consistent across identical runs of a program with the same input. 
While machine instructions could serve this purpose for a single binary, Nugget instead counts executed LLVM IR instructions as its unit of work. 
This ensures a uniform measurement of program progress across all binaries of the same program with the same input.

A unit of work directly determines the notion of intervals. 
For example, if the unit of work is the number of executed instructions, then each interval corresponds to a fixed number of executed instructions during runtime. 
A sample is a specific interval of a program's execution; thus, the unit of work also defines what constitutes a sample.

The choice of unit of work influences not only how intervals are defined, but also the sample selection algorithm and the statistical models used in performance prediction. 
Therefore, the unit of work must be defined consistently across all binaries to ensure that samples remain independent of any specific binary.
For example, if the unit of work is the number of executed machine-level instructions, then the sample will be tied to a specific binary because any binary changes can affect the number of machine-level instructions executed, even if the control flow remains the same~\cite{cross_binary_simpoints}.

LLVM~\cite{llvm} is an open-source compiler infrastructure that transforms source code into a platform-independent intermediate representation (IR) before generating machine-specific binaries.
LLVM IR instructions abstract away the underlying machine-level instructions, so as long as the control flow remains the same at the LLVM IR level, the definition of all intervals of program execution remains consistent across different binaries.
Since LLVM IR instructions are an abstraction of machine-level instructions, the number of executed LLVM IR instructions reflects the progress of program execution just as the number of executed machine-level instructions does.

\shepherd{
Therefore, Nugget's unit of work is suitable for applications that have stable control flow across different platforms.
Applications such as gradient descent, where floating-point precision might affect the control flow, are not suitable for Nugget or for any sampling methodologies that rely on the application having stable control flows across microarchitectures~\cite{wavelet-based,simpoint,looppoint,cross_binary_simpoints,pacsim,barrier_point,simpoint-plus,parrot}.}
